---
title: "Assignment 1"
output: pdf_document
---

##Loading Iris dataset

```{r}
install.packages("data.table")          #to add if require part
library("data.table")
Iris.dt<-setDT(iris)
class(Iris.dt)

library("corrplot")

```
##Question 1
```{r}
Irischar<-Iris.dt[,1:4]
Iriscorr<-cor(Irischar)
Iriscorrplot<-corrplot(Iriscorr, type="upper", order="hclust",method="circle",addCoef.col = "Green")

```
As per the above plot, petal.length and petal.width has the highest correlation coefficient of 0.96 showing strong positive relationship

##Question 2
```{r}

```
1) Correlation coefficients do not provide causation for the relationship. In addition, the correlation coefficient only looks at linear relationships. For example, a vehicle requires gasoline to drive. The correlation is positive for high volume of gasoline to duration and/or distance the vehicle drives. However, this does not take into account the type of gas. This additional variable has a significant impact on the relationship but would not be identified in a correlation coefficient.

##Question 3
```{r}
Irismean<-sapply(Filter(is.numeric, Iris.dt), mean)
Irismean

