---
title: "Assignment 1"
output: pdf_document
---
##Loading required packages
```{r}
if(!require("pacman")) install.packages("pacman")
pacman::p_load(esquisse, forecast, tidyverse, 
               gplots, GGally, gganimate,
               mosaic, scales, mosaic, mapproj, mlbench, data.table)
library("corrplot")
search()
theme_set(theme_classic())
```

##Loading Iris dataset

```{r}
data("iris")
#checking class of iris dataset
class("iris")
#Converting to data.table 
Iris.dt<-setDT(iris)
class(Iris.dt)

```
##Question 1
```{r}
#Keeping only numeric variables
Irisnum.dt <- Filter(is.numeric, Iris.dt)

#computing correlation of numeric variables
Iriscorr<-cor(Irisnum.dt)

#Visualizing the correlation matrix
Iriscorrplot<-corrplot(Iriscorr, type="upper", order="hclust",method="circle",addCoef.col = "Green")

```
As per the above plot, petal length and petal width has the highest correlation coefficient of 0.96 indicating strong positive linear relationship.

##Question 2
1) Correlation coefficients do not provide causation for the relationship. In addition, the correlation coefficient only looks at linear relationships. For example, a vehicle requires gasoline to drive. The correlation is positive for high volume of gasoline to duration and/or distance the vehicle drives. However, this does not take into account the type of gas. This additional variable has a significant impact on the relationship but would not be identified in a correlation coefficient.

##Question 3
```{r}
#Keeping only numeric variables
Irisnum.dt <- Filter(is.numeric, Iris.dt)

#Calculating mean
Irismean<-sapply(Irisnum.dt, mean)
Irismean
```
```{r}
#Checking maximum of calculated mean
max(Irismean)
```
Sepal.length variable has the highest mean of 5.843333

##Question 4
```{r}
ggplot(Iris.dt, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point()+
ggtitle("Correlation b/w Sepal Length and Sepal Width")+
   ylab("Sepal Width")+
  xlab("Sepal Length")
```

##Question 5
```{r}
ggplot(Iris.dt, aes(x=Petal.Length, y=Petal.Width, color=Species)) +
  geom_point()+
  ggtitle("Correlation b/w Petal Length and Petal Width")+
  ylab("Petal Width")+
  xlab("Petal Length")
  
