---
title: "Assignment 1"
output: pdf_document
---
##Loading required packages
```{r loadpackages}
if(!require("pacman")) install.packages("pacman")
pacman::p_load(esquisse, forecast, tidyverse, 
               gplots, GGally, gganimate,
               mosaic, scales, mosaic, mapproj, mlbench, data.table)
install.packages("corrplot")
library("corrplot")
search()
theme_set(theme_classic())
```

##Loading Iris dataset

```{r Iris Data Table}
data("iris")
#checking class of iris dataset
class("iris")
#Converting to data.table 
Iris.dt<-setDT(iris)
class(Iris.dt)

```
##Question 1
```{r Question 1}
#Keeping only numeric variables
Irisnum.dt <- Filter(is.numeric, Iris.dt)

#computing correlation of numeric variables
Iriscorr<-cor(Irisnum.dt)

#Visualizing the correlation matrix
Iriscorrplot<-corrplot(Iriscorr, type="upper", order="hclust",method="circle",addCoef.col = "Green")

```
As per the above plot, petal length and petal width has the highest correlation coefficient of 0.96 indicating strong positive linear relationship.

##Question 2
1) Correlation coefficients do not provide causation for the relationship. In addition, the correlation coefficient only looks at linear relationships. For example, a vehicle requires gasoline to drive. The correlation is positive for high volume of gasoline to duration and/or distance the vehicle drives. However, this does not take into account the type of gas or type of car being driven. The correlation for one brand of car with 15 gallons of gas may be stronger due it driving further, but another brand of car might have have 20 gallons of gas and drive a less distance due to the type of gas and MPG. The addition of variables have a significant impact on the relationship but would not be identified in a correlation coefficient.

##Question 3
```{r Mean}
#Keeping only numeric variables
Irisnum.dt <- Filter(is.numeric, Iris.dt)

#Calculating mean
Irismean<-sapply(Irisnum.dt, mean)
Irismean
```
```{r}
#Checking maximum of calculated mean
max(Irismean)
```
Sepal.length variable has the highest mean of 5.843333

##Question 4
```{r Sepal Relationship}
ggplot(Iris.dt, aes(x=Sepal.Length, y=Sepal.Width, color=Species)) +
  geom_point()+
ggtitle("Correlation b/w Sepal Length and Sepal Width")+
   ylab("Sepal Width")+
  xlab("Sepal Length")
```

##Question 5
```{r Petal Relatioship}
ggplot(Iris.dt, aes(x=Petal.Length, y=Petal.Width, color=Species)) +
  geom_point()+
  ggtitle("Correlation b/w Petal Length and Petal Width")+
  ylab("Petal Width")+
  xlab("Petal Length")
```


##Question 6 
The Petal Length and Petal Width combination provides a better separation of records between the two graphs becuase the variables of Petal Length and Petal Width are more highly correlated (0.96) than Sepal Length and Width (-0.12). The Petal graph in question 5 represents lower error rate when calculating the relationship using predictive variable between petal length and petal width, resulting in more defined clusteres per species. In addition there is significant overlap between Versicolor and Virginica species in the Sepal graph in question 4. The high error rate in this graph makes it difficult to classify the species using these specific variables. 

##Question 7 
```{r Confusion Matrix Accuracy}
(2+5)/100 #overall error rate
1-.07 #accuracy percentage

```
##Question 7 Explanation
Calculating the actual classifications of each species, we gather the sum of each species and found they are equal [Versicolor = 50, Setosa = 50]. This means our NIR is .50. 

Comparing the NIR (0.50) and the accuracy percentage of (0.93), the accuracy of the model is greater than the NIR. We can conclude that the current model can predict the calssifications 43% better than the NIR.

##Question 8 
``` {r Sensitivity}

Sensitivity <- 45 / (45 + 5);Sensitivity

#Sensitivity = (TP / (TP + FN)) = 45 / (45 + 5) = 45 / 50 -> 0.9 (90%)
```

##Question 9 
``` {r Specificity}

Specificity <- 48 / (48 + 2);Specificity
#Specificity = (TN / (TN + FP)) = 48 / (48 + 2) = 48 / 50 -> 0.96 (96%)
```

##Question 10 
``` {r Precision}
Precision <- 45 / (45 + 2);Precision
#Precision = (TP / (TP + FP)) = 45 / (45 + 2) = 45 / 47 -> 0.9574 (95.74%)

```
